Capstone Movielens Report

### 2025-12-25 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Fix for Report section: UMGYDE Model Tuning by `degree` and `span` Parameters.

Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three stages - one for each possible value of the `degree`.

For each value of the `degree` parameter, we will divide each stage into the following two steps for tuning the model by the `span` parameter:

>>>>

Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three stages - one for each value.

In addition, we will divide each stage into the following two steps for tuning the model by the `span` parameter:
